---
title: "BEES3041 Canopy Height"
author: "Gillian"
date: "03/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# __Study Aim:__ 
To investigate the bimodality in canopy height distribution in the intermediate rainfall zone (1500-2000mm).  

## __Examine the role of:__
* Human disturbance
* Biome classification 
* Fire size


## __Data Processing__  


__Load libraries__
```{r}
library(tidyverse)
library(png)
library(raster)
library(rgdal)
library(ncdf4)
library(sf)
library(sp)
library(readxl)
```


*Source data proccessing file with precreated functions to load the datasets*
```{r}
source("R/data_processing.R")
```


__Loading data and creating a combined dataframe:__
```{r, eval=FALSE}
data_height <- get_height_df()

data_precip <- get_precip_df()

data_treecover <- get_tree_cover_df()

data_globcover <- get_area_type_df()

data_intactforest <- get_intactforest_df()

data_all <-
  init_globe_df() %>%
  left_join(by = c("x", "y"), data_height) %>%
  left_join(by = c("x", "y"), data_precip) %>%
  left_join(by = c("x", "y"), data_treecover) %>%
  left_join(by = c("x", "y"), data_globcover) %>%
  left_join(by = c("x", "y"), data_intactforest) %>%
  mutate(forest_zone = percentage_tree_cover >= 20)

saveRDS(data_all, "data/data_all.rds")
```


```{r}
data_all <- readRDS("data/data_all.rds")
```


__Subsetting Data to only include only areas with >20% vegetation cover and with a 'forest' biome classification and in rainfall zone 1500-2000mm.__
```{r}
data_all_graphing <-
  subset(data_all,
         canopy_height > 1 &
           percentage_tree_cover > 0.001 & forest_zone == "TRUE")

data_subset_graphing <-
  subset(
    data_all_graphing,
    forest_zone == "TRUE" &
      globcover_numeric != "11" &
      globcover_numeric != "14" &
      globcover_numeric != "20" &
      globcover_numeric != "30" &
      globcover_numeric != "190" &
      globcover_numeric != "200" &
      globcover_numeric != "210" &
      globcover_numeric != "220" &
      globcover_numeric != "230" &
      globcover_numeric != "150" &
      !is.na(data_all_graphing$globcover_numeric)
  )

rain_gap <-
  data_subset_graphing %>% filter(mean_annual_precipitation < 2000) %>%
  filter(mean_annual_precipitation > 1500)

```


## __Visualising Data__  


__Precipitation count graphs for all data and subset data:__
```{r}
# Count for all data
ggplot(data_all, aes(mean_annual_precipitation)) +
  geom_freqpoly(stat = "bin") +
  scale_x_continuous(limits = c(0, 4000))

# Count for forest subsetted data
ggplot(data_subset_graphing, aes(mean_annual_precipitation)) +
  geom_freqpoly(stat = "bin") +
  scale_x_continuous(limits = c(0, 4000))
```


__Visualizing intactness and canopy height Data through recreating Scheffer et al (2018) and Falster et al (unpublished)'s graphs.__
```{r}
library(ggplot2)
library(tidyverse)
library(viridis)

#Recreating Scheffer et al (2018) density plot

ggplot(data_subset_graphing,
       aes(mean_annual_precipitation, canopy_height)) +
  geom_bin2d() +
  scale_fill_viridis(option = "turbo") +
  scale_x_continuous(expand = c(0, 0), limit = c(0, 3500)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() + ggtitle(expression(
    underline("Precipitation and Global Canopy Height Distribution")
  )) + labs(y = "Canopy Height (m)", x = "Mean Annual Precipitation (mm)", caption = "Figure 1: Reconstruction of the Scheffer et al. (2018) density plot showing the \ndistinct jump in canopy height at 1500mm precipitation.") + labs(fill = "Density Count") + theme(
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    plot.caption = element_text(hjust = 0, size = 10),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10)
  )
ggsave("recreation_scheffer.png",
       width = 10,
       height = 6,
)

#Recreating Falster et al (unpublished) density plot separating intact vs non intact

ggplot(data_subset_graphing,
       aes(mean_annual_precipitation, canopy_height)) +
  geom_bin2d() + scale_fill_viridis(option = "turbo") + facet_wrap( ~ intact_forest) + scale_x_continuous(expand = c(0, 0), limits = c(0, 3500)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() +
  theme_classic() + ggtitle(expression(underline(
    "Canopy Height, Precipitaton and Intactness"
  ))) + labs(y = "Canopy Height (m)", x = "Mean Annual Precipitation (mm)", caption = "Figure 2: Density plots showing the relationship between precipitation and canopy height for intact and\n non-intact forests.The graphs show a significant difference in canopy height distribution between intact\n and non-intact forests.") + labs(fill = "Density Count") + theme(
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    plot.caption = element_text(hjust = 0, size = 10),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10),
    strip.text = element_text(size = 10)
  )
ggsave("recreation_falsterintactnon.png",
       width = 10,
       height = 6,
)
```


__Investigating If Land Cover Classification Could Have A Relationship with Canopy Height.__ *Decided not to further investigate*
```{r}
ggplot(data_all_graphing,
       aes(mean_annual_precipitation, canopy_height)) +
  geom_point(size = 0.05,
             alpha = 0.3,
             aes(colour = globcover_label)) +
  scale_x_continuous(limits = c(0, 4000)) + theme(legend.position = "none")


## removing pesky "NA" values
is.na_remove <- subset(data_subset_graphing,!is.na(data_subset_graphing$globcover_label))

ggplot(is.na_remove, aes(mean_annual_precipitation, canopy_height)) +
  scale_x_continuous(limits = c(0, 4000)) +
  geom_density_2d_filled() +
  facet_wrap(vars(globcover_label))


#graphing biomes
ggplot(is.na_remove, aes(mean_annual_precipitation, canopy_height)) +
  geom_density_2d(aes(colour = globcover_label)) + theme(legend.position = "none")


# Map to show distribution of biomes
world <- map_data("world")

ggplot() +
  geom_map(
    data = world,
    map = world,
    aes(long, lat, map_id = region),
    color = "white",
    fill = "lightgray",
    size = 0.1
  ) +
  geom_point(
    data = rain_gap,
    aes(x, y, colour = globcover_label),
    alpha = 0.4,
    size = 0.1
  ) + theme(legend.position = "none") #remove legend expression to see legend

#Frequency Distribution of biomes in 1500-2000mm rainfall zone
ggplot(rain_gap, aes(globcover_numeric)) +
  geom_histogram(stat = "count")


#Frequency Distribution of biomes for all rainfall zones
ggplot(data_subset_graphing, aes(globcover_numeric)) +
  geom_histogram(stat = "count")

```


__Mapping canopy height and intactness to visualise global patterns in distribution:__
```{r}
## turning height into a categorical variable (0-25=small 25-30=medium 30-> tall)
height_cat <-
  cut (
    rain_gap$canopy_height,
    breaks = c(0, 25, 30, 60),
    labels = c("small", "medium", "tall")
  )
rain_gap$height_cat <- height_cat


##Mapping the global distribution of canopy height categories
world <- map_data("world")

ggplot() +
  geom_map(
    data = world,
    map = world,
    aes(long, lat, map_id = region),
    color = "white",
    fill = "lightgray",
    size = 0.1
  ) +
  geom_point(
    data = rain_gap,
    aes(x, y, colour = height_cat),
    alpha = 0.4,
    size = 0.1
  )


## Mapping the distribution of intact and non-intact forests
ggplot() +
  geom_map(
    data = world,
    map = world,
    aes(long, lat, map_id = region),
    color = "white",
    fill = "lightgray",
    size = 0.1
  ) +
  geom_point(
    data = rain_gap,
    aes(x, y, colour = intact_forest),
    alpha = 0.4,
    size = 0.1
  ) 
```


## __Data Processing__


__Loading Fire Data to Help Explain Canopy Bimodality__ 
```{r}
load_fire <- function(year) {
  path <- paste0("data/firedata/", year, "firesize.tif")
  
  e <- set_extent()
  
  raster::stack(path) %>%
    sum() %>%
    crop(e) %>%
    raster::as.data.frame(xy = TRUE) %>%
    as_tibble() %>%
    mutate(year = year)
}

## (run in analysis for file location)

fire_2003 <- load_fire(2003)
fire_2004 <- load_fire(2004)
fire_2005 <- load_fire(2005)
fire_2006 <- load_fire(2006)
fire_2007 <- load_fire(2007)
fire_2008 <- load_fire(2008)
fire_2009 <- load_fire(2009)
fire_2010 <- load_fire(2010)
fire_2011 <- load_fire(2011)
fire_2012 <- load_fire(2012)
fire_2013 <- load_fire(2013)
fire_2014 <- load_fire(2014)
fire_2015 <- load_fire(2015)
fire_2016 <- load_fire(2016)

#Joining yearly fire Data into a single dataframe

all_fire <-
  rbind(
    fire_2003,
    fire_2004,
    fire_2005,
    fire_2006,
    fire_2007,
    fire_2008,
    fire_2009,
    fire_2010,
    fire_2011,
    fire_2012,
    fire_2013,
    fire_2014,
    fire_2015,
    fire_2016
  )

#Calculating total burnt area and mean burnt area

fire_sum <-
  all_fire %>% group_by(x, y) %>% summarise(total_burnt_area = sum(layer))

fire_average <-
  all_fire %>% group_by(x, y) %>% summarise(mean_burnt_area = mean(layer))
```


Changing the downscale function:
```{r}
downscale_spatial_data_.5 <- function(rl, func = "mean") {
  cells.per.degree <- rl@ncols / (xmax(extent(rl) - 1) - xmin(extent(rl) -
                                                                1))
  factor <- cells.per.degree / 2
  
  # perform downscale and return resultant RasterLayer
  if (factor > 1)
    rl <- aggregate(rl,
                    fact = factor,
                    fun = func)
  rl
}
```


Rescaling the sum and average columns:
```{r}
#fire sum rescale
coordinates(fire_sum) <- ~ x + y
gridded(fire_sum) <- TRUE
raster_sum_fire <- raster(fire_sum)

rescale_sum_fire <- downscale_spatial_data_.5(raster_sum_fire)

e <- set_extent()

rescale_sum_fire <- raster::stack(rescale_sum_fire) %>%
  sum() %>%
  crop(e) %>%
  raster::as.data.frame(xy = TRUE) %>%
  as_tibble()


#fire average rescale
coordinates(fire_average) <- ~ x + y
gridded(fire_average) <- TRUE
raster_average_fire <- raster(fire_average)

rescale_average_fire <-
  downscale_spatial_data_.5(raster_average_fire)

e <- set_extent()

rescale_average_fire <- raster::stack(rescale_average_fire) %>%
  sum() %>%
  crop(e) %>%
  raster::as.data.frame(xy = TRUE) %>%
  as_tibble()

```

__Joining the fire data with the rest of the data:__
```{r}
data_all_withfire <-
  data_all %>%
  left_join(by = c("x", "y"), rescale_sum_fire)

data_all_withfire <-
  data_all_withfire %>%
  left_join(by = c("x", "y"), rescale_average_fire)

data_all_withfire_graphing <-
  subset(
    data_all_withfire,
    canopy_height > 1 &
      percentage_tree_cover > 0.001 & forest_zone == "TRUE"
  )

data_subset_withfire_graphing <-
  subset(
    data_all_withfire_graphing,
    forest_zone == "TRUE" &
      globcover_numeric != "11" &
      globcover_numeric != "14" &
      globcover_numeric != "20" &
      globcover_numeric != "30" &
      globcover_numeric != "190" &
      globcover_numeric != "200" &
      globcover_numeric != "210" &
      globcover_numeric != "220" &
      globcover_numeric != "230" &
      globcover_numeric != "150" &
      !is.na(data_all_withfire_graphing$globcover_numeric)
  )

#Creating dataframe that includes fire just for the Intermediate Rainfall Zone

rain_gap_fire <-
  data_subset_withfire_graphing %>% filter(mean_annual_precipitation < 2000) %>%
  filter(mean_annual_precipitation > 1500)

```


## __Visualising Data__


__Graphing the raw fire data to understand its distribution.__
```{r}
#Visualising the mean annual fire size and total fire size in relation to canopy height and precipitation

ggplot(data_subset_withfire_graphing, aes(canopy_height, mean_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 60))

ggplot(data_subset_withfire_graphing, aes(canopy_height, mean_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 60)) + scale_y_log10()

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, mean_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 4000))

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, mean_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 4000)) + scale_y_log10()


ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, total_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 4000))

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, total_burnt_area)) + 
  geom_point(size=0.05) + 
  scale_x_continuous(limits = c(0, 4000)) + scale_y_log10()
```

__Visualising the interaction between variables.__
```{r}
#Creating a burnt column for fire data to record areas a fire has passed through 
data_subset_withfire_graphing$burnt <- if_else(data_subset_withfire_graphing$mean_burnt_area > 0, "burnt", "unburnt")


#graphing the relationship between canopy height and preciptiation and colouring by burnt or unburnt
ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height )) +
  geom_point(size=0.05, alpha=0.3, aes(colour=burnt)) + 
  scale_x_continuous(limits = c(0, 4000))

#graph showing burnt area and canopy height relationship
ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height )) +
   geom_density_2d(aes(colour = burnt))

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~burnt)+ scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), limit = c(0, 2500)) +
  theme_classic()


#burnt vs unburnt for canopy height/cover
ggplot(data_subset_withfire_graphing, aes(percentage_tree_cover, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~burnt)+ scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic()


#Density plot burnt area and canopy height
ggplot(data_subset_withfire_graphing, aes(mean_burnt_area, canopy_height)) + 
  geom_bin2d()+
  scale_fill_viridis(option = "turbo")+
  scale_x_continuous(expand = c(0, 0), limit = c(0, 1000)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() + scale_x_log10()

#Mapping burnt and unburnt areas in rainfall zone 1500-200mm, showing most areas have been burnt
fire_distribution_rainfallzone <- data_subset_withfire_graphing %>% filter(mean_annual_precipitation < 2000, mean_annual_precipitation > 1500)

ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "white", fill = "lightgray", size = 0.1
    ) +
  geom_point(
    data = fire_distribution_rainfallzone,
    aes(x, y, colour=burnt),
    alpha = 0.4, size = 0.1
  )
```

__Graphing the effect of fire and intactness on canopy height:__
```{r}
#mean burnt area and canopy height by intact vs non intact
ggplot(data_subset_withfire_graphing, aes(mean_burnt_area, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~intact_forest)+ scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() + scale_x_continuous(expand = c(0, 0), limit= c(0, 1000)) +
  scale_y_continuous(expand = c(0, 0), limit = c(0, 40)) +
  theme_classic()

ggplot(data_subset_withfire_graphing, aes(mean_burnt_area, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~intact_forest)+ scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() + scale_x_continuous(expand = c(0, 0), limit= c(0, 1000)) +
  scale_y_continuous(expand = c(0, 0), limit = c(0, 40)) +
  theme_classic() + scale_x_log10()

ggplot(data_subset_withfire_graphing, aes(mean_burnt_area, mean_annual_precipitation)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~intact_forest)+ scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_classic() + scale_x_continuous(expand = c(0, 0), limit= c(0, 1000)) +
  scale_y_continuous(expand = c(0, 0), limit = c(0, 2500)) +
  theme_classic()
```


__Creating a new variable of big fire or little/no fire because most cells had some level of burnt.__
```{r}
#Dividing fire data into big and small/no fire categories

data_subset_withfire_graphing$firesize <- if_else(data_subset_withfire_graphing$mean_burnt_area > 1.25, "big_fire", "small_no_fire")

rain_gap_fire$firesize <- if_else(rain_gap_fire$mean_burnt_area > 1.25, "big_fire", "small_no_fire")


#Comparing use of burnt and unburnt values with new values that divide by big and small fire

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~firesize)+ scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), limit = c(0, 2500)) +
  theme_classic()

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height)) +
  geom_bin2d()+ scale_fill_viridis(option = "turbo") + facet_wrap(~burnt)+ scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0), limit = c(0, 2500)) +
  theme_classic()

ggplot(rain_gap_fire, aes(mean_annual_precipitation, canopy_height )) +
	   geom_density_2d(aes(colour = firesize))

```

__Looking at interaction between precipitation, fire, intactness and canopy height__
```{r}
ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height)) + 
  geom_point(size=0.05, aes(colour=intact_forest)) +  scale_x_continuous(limit = c(0, 2500)) + facet_wrap(~firesize)

ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height)) + 
  geom_point(size=0.05, aes(colour=intact_forest)) +  scale_x_continuous(limit = c(0, 2500)) + facet_wrap(~burnt)


ggplot(rain_gap_fire, aes(mean_annual_precipitation, canopy_height)) + 
  geom_point(size=0.05, aes(colour=intact_forest)) +  scale_x_continuous(limit = c(1500, 2000)) + facet_wrap(~firesize)

	
	ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height )) +
   geom_density_2d(aes(colour = intact_forest)) +  
   scale_x_continuous(limits = c(1500, 2000)) +
   facet_wrap(~firesize)


ggplot(data_subset_withfire_graphing, aes(mean_annual_precipitation, canopy_height )) +
   geom_density_2d(aes(colour = firesize)) +  
   scale_x_continuous(limits = c(1500, 2000)) +
   facet_wrap(~intact_forest)
```


## __FINDINGS__


__Mapping the distribution of variables to compare patterns:__
```{r}
rain_gap_fire$firesize <- if_else(rain_gap_fire$mean_burnt_area > 1.25, "big_fire", "small_no_fire")

world <- map_data("world")

#Mapping the distribution of fires 

ggplot() +
  geom_map(
    data = world,
    map = world,
    aes(long, lat, map_id = region),
    color = "white",
    fill = "lightgray",
    size = 0.1
  ) +
  geom_point(
    data = rain_gap_fire,
    aes(x, y, colour = firesize),
    alpha = 0.4,
    size = 0.1
  ) + ggtitle("Global Distribution Fire Regimes Across Forests in Intermediate Rainfall Zone")+ labs(colour = "Fire Size") + theme(plot.title = element_text(hjust = 0.5))

ggsave("firemap.jpg", width = 15,
  height = 7,)


#Mapping forest intactness

ggplot() +
  geom_map(
    data = world,
    map = world,
    aes(long, lat, map_id = region),
    color = "white",
    fill = "lightgray",
    size = 0.1
  ) +
  geom_point(
    data = rain_gap_fire,
    aes(x, y, colour = intact_forest),
    alpha = 0.4,
    size = 0.1
  ) + ggtitle("Global Distribution of Intact and Non Intact Forests")+ labs(colour = "Forest Intactness") + theme(plot.title = element_text(hjust = 0.5))
ggsave("intactmap.jpg", width = 15, height = 7)


#Mapping the distribution of canopy heights

ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "white", fill = "lightgray", size = 0.1
    ) +
  geom_point(
    data = rain_gap,
    aes(x, y, colour=height_cat),
    alpha = 0.4, size = 0.1
  ) + ggtitle("Global Distribution of Canopy Height")+ labs(colour = "Forest Height") + theme(plot.title = element_text(hjust = 0.5))

ggsave("small_medium_tall.jpg", width = 15,
  height = 7,)
```



__Density graphs that best display findings and support hypotheses:__
```{r}
#Renaming the big and small fire variables as the new burnt and unburnt values for the subsetted all data.

data_subset_withfire_graphing$firesize <-
  if_else(data_subset_withfire_graphing$mean_burnt_area > 1.25,
          "Burnt",
          "Unburnt")

#Contour density graph showing the effect of precipitation, fire and intactness on canopy height

ggplot(data_subset_withfire_graphing,
       aes(mean_annual_precipitation, canopy_height)) +
  geom_density_2d(aes(colour = intact_forest)) +
  scale_x_continuous(limits = c(1500, 2000)) +
  facet_wrap(~ firesize) + ggtitle("Canopy Height, Precipitaiton, Fire Size and Forest Intactness") + labs(
    y = "Canopy Height (m)",
    x = "Mean Annual Precipitation (mm)",
    caption = "add caption!",
    colour = "Forest Intactness"
  ) + theme(
    plot.title = element_text(hjust = 0.5, size = 50, face = "bold"),
    plot.caption = element_text(hjust = 0, size = 35),
    axis.text = element_text(size = 40),
    axis.title = element_text(size = 40),
    legend.text = element_text(size = 35),
    legend.title = element_text(size = 35),
    strip.text = element_text(size = 40),
    strip.background = element_rect(
      fill = "white",
      colour = "white",
      size = 1
    )
  ) + theme_classic()
ggsave("main_graph.png", width = 7,
       height = 4)


#The relationship between mean burnt area and mean annual precipitation in the intermediate rainfall zone

ggplot(rain_gap_fire, aes(mean_annual_precipitation, mean_burnt_area))  +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_viridis(option="H") + scale_y_log10()+ ggtitle("                   Fire Size and Precipitation") + labs(y = "Mean Burnt Area (km²)", x = "Mean Annual Precipitation (mm)", caption = "__") + theme(legend.position='none', plot.title = element_text(hjust = 0.5), plot.caption = element_text(hjust = 0)) + theme_classic() 
ggsave("fire_and_rain.png", width = 6,
  height = 4,)


#The relationship between mean burnt area and canopy height

ggplot(rain_gap_fire, aes(mean_burnt_area, canopy_height)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_viridis(option="H") + theme(legend.position='none') +scale_x_log10()+ggtitle("            Mean Burnt Area and Canopy Height") + labs(y = "Canopy Height (m)", x = "Mean Burnt Area", caption = "Density plot showing the relationship between canopy height (m) and mean burnt area") + theme(plot.title = element_text(hjust = 10), plot.caption = element_text(hjust = 0)) + theme_classic() 
ggsave("fire_and_height.png", width = 6,
       height = 4)

```
